```{r, include = FALSE}
require(plyr)

full = read.csv("C:/Users/RLP/Downloads/Table_1_PValue_Study.csv",skip = 1)
full2 = rename(full,c("What.is.your.name." = "name","What.type.of.trial.is.this." = "Type","How.many.individuals.were.enrolled.in.this.study." = "N", "Is.there.a.baseline.characteristics.table." = "Table","If.no..is.there.any.suggestion.in.the.text.that.the.authors.used.statistics.to.compare.baseline.d....Yes..p.value.mentioned"="No_Tab_TextP",
"If.no..is.there.any.suggestion.in.the.text.that.the.authors.used.statistics.to.compare.baseline.d....No" ="No_Tab_TextN",
"If.no..is.there.any.suggestion.in.the.text.that.the.authors.used.statistics.to.compare.baseline.d....Yes..see.text.pasted.below" = "No_Tab_TextT", "If.no..is.there.any.suggestion.in.the.text.that.the.authors.used.statistics.to.compare.baseline.d....Yes..confidence.intervals.or.standard.error.mentioned"="No_Tab_TextC",
"Are.p.values.presented.in.the.baseline.characteristics.table..Yes..p.value" = "TabP",
"Are.p.values.presented.in.the.baseline.characteristics.table..No" = "TabN",
"Are.p.values.presented.in.the.baseline.characteristics.table..Unclear..please.explain." = "TabT","Are.p.values.presented.in.the.baseline.characteristics.table..Yes..significance.testing.referenced"= "TabG", "Are.p.values.presented.in.the.baseline.characteristics.table..Yes..confidence.intervals.or.standard.error" = "TabC",
"Any.other.comments.about.the.study.that.confused.you.or.you.would.like.to.comment.on." = "Comments","Article.Number" = "Article", "Year.of.Publication" = "Year"))
proper_data = data.frame(Name = full2$name, Article = full2$Article, Year = full2$Year, Type = full2$Type, N = full2$N, Table = full2$Table,TabP = full2$TabP,TabC = full2$TabC,TabT = full2$TabT,TabN = full2$TabN, TabG = full2$TabG, No_Tab_TextP = full2$No_Tab_TextP,No_Tab_TextN = full2$No_Tab_TextN,No_Tab_TextT = full2$No_Tab_TextT,No_Tab_TextC = full2$No_Tab_TextC,Comments = full2$Comments)

proper_data$TabC = proper_data$TabC + 1
proper_data$TabT = proper_data$TabT + 2
proper_data$TabG = proper_data$TabG + 3
proper_data$TabN = proper_data$TabN + 4
proper_data$No_Tab_TextC = proper_data$No_Tab_TextC + 1
proper_data$No_Tab_TextT = proper_data$No_Tab_TextT + 2
proper_data$No_Tab_TextN = proper_data$No_Tab_TextN + 3
proper_data[is.na(proper_data)] <- 0

proper_data2 = transform(proper_data, tab_sig = TabP + TabC + TabT + TabN + TabG, no_tab = No_Tab_TextP + No_Tab_TextC + No_Tab_TextT + No_Tab_TextN)

proper_data3 = data.frame(Name = proper_data2$Name, Article = proper_data2$Article, Type = proper_data2$Type, N = proper_data2$N, Table = proper_data2$Table,tab_sig = proper_data2$tab_sig, no_tab = proper_data2$no_tab,Comments = proper_data2$Comments, Year = proper_data2$Year)
proper_data3[proper_data3 == 0] <- NA

subR = subset(proper_data3, Name == 1)
subM = subset(proper_data3, Name == 3)

subR2 = rename(subR, c("Year" = "Year_R", "Type" = "Type_R", "N" = "N_R", "Table" = "Table_R", "tab_sig" = "tab_sig_R", "no_tab" = "no_tab_R", "Comments" = "Comments_R"))
subM2 = rename(subM, c("Year" = "Year_M", "Type" = "Type_M", "N" = "N_M", "Table" = "Table_M", "tab_sig" = "tab_sig_M", "no_tab" = "no_tab_M", "Comments" = "Comments_M"))
R_half = data.frame(Article = subR2$Article, Year_R = subR2$Year_R, Type_R = subR2$Type_R, N_R = subR2$N_R, Table_R = subR2$Table_R, tab_sig_R = subR2$tab_sig_R, no_tab_R = subR2$no_tab_R, Comments_R = subR2$Comments_R)
M_half = data.frame(Article = subM2$Article,Year_M = subM2$Year_M,Type_M = subM2$Type_M, N_M = subM2$N_M, Table_M = subM2$Table_M, tab_sig_M = subM2$tab_sig_M, no_tab_M = subM2$no_tab_M, Comments_M = subM2$Comments_M)

# Cleaned complete dataset
final_data = merge(R_half,M_half,by="Article", all = TRUE)

# Disagree on type of trial
diff_Type = data.frame(Article = final_data$Article[final_data$Type_R != final_data$Type_M],Type_R = final_data$Type_R[final_data$Type_R != final_data$Type_M],Type_M = final_data$Type_M[final_data$Type_R != final_data$Type_M])
diff_Type

which(is.na(final_data$Type_M))

# Disagree on Year of Publication
t_Type = data.frame(Article = final_data$Article[final_data$Year_R != final_data$Year_M],Year_R = final_data$Year_R[final_data$Year_R != final_data$Year_M],Year_M = final_data$Year_M[final_data$Year_R != final_data$Year_M])
t_Type

# Disagree on sample size
N_Type = data.frame(Article = final_data$Article[final_data$N_R != final_data$N_M],N_R = final_data$N_R[final_data$N_R != final_data$N_M],N_M = final_data$N_M[final_data$N_R != final_data$N_M])
N_Type

table(final_data$N_M,exclude=NULL)

# Subset of articles where we agreed on type of trial
agree = final_data[!final_data$Article%in%diff_Type$Article,] 

# Disagree on whether baseline table is present
agree_DT = data.frame(Article = agree$Article[agree$Table_R != agree$Table_M & agree$Type_R < 4], Table_R = agree$Table_R[agree$Table_R != agree$Table_M & agree$Type_R < 4], Table_M = agree$Table_M[agree$Table_R != agree$Table_M & agree$Type_R < 4])
agree_DT

# Subset of article where we agreed on presence of baseline table
agree_AT = agree[!agree$Article%in%agree_DT$Article,]

# Data where we agreed on type of trial, presence of table
agree_ATS = subset(agree_AT, Table_R == 1 & Type_R < 5)

# Data where we agreed on type of trial, no presence of table
agree_ATT = subset(agree_AT, Table_R == 2 & Type_R < 5)

# Disagree on presence of significance testing in baseline table
agree_ATA = data.frame(Article = agree_ATS$Article[agree_ATS$tab_sig_R != agree_ATS$tab_sig_M], tab_sig_R = agree_ATS$tab_sig_R[agree_ATS$tab_sig_R != agree_ATS$tab_sig_M], tab_sig_M = agree_ATS$tab_sig_M[agree_ATS$tab_sig_R != agree_ATS$tab_sig_M])
agree_ATA

# Disagree on presence of significance testing in text
agree_ATB = data.frame(Article = agree_ATS$Article[agree_ATS$no_tab_R != agree_ATS$no_tab_M], Text_R = agree_ATS$no_tab_R[agree_ATS$no_tab_R != agree_ATS$no_tab_M], Text_M = agree_ATS$no_tab_M[agree_ATS$no_tab_R != agree_ATS$no_tab_M])
agree_ATB[complete.cases(agree_ATB * 0), , drop=FALSE]

# Disagree on sample size
agree_ATX = data.frame(Article = agree_ATS$Article[agree_ATS$N_R != agree_ATS$N_M], N_R = agree_ATS$N_R[agree_ATS$N_R != agree_ATS$N_M], N_M = agree_ATS$N_M[agree_ATS$N_R != agree_ATS$N_M])
agree_ATX
agree_ATY = data.frame(Article = agree_ATT$Article[agree_ATT$N_R != agree_ATT$N_M], N_R = agree_ATT$N_R[agree_ATT$N_R != agree_ATT$N_M], N_M = agree_ATT$N_M[agree_ATT$N_R != agree_ATT$N_M])
agree_ATY

# Disagree on in-text reference to statistical tests
agree_ATO = data.frame(Article = agree_ATT$Article[agree_ATT$no_tab_R != agree_ATT$no_tab_M], no_tab_R = agree_ATT$no_tab_R[agree_ATT$no_tab_R != agree_ATT$no_tab_M], no_tab_M = agree_ATT$no_tab_M[agree_ATT$no_tab_R != agree_ATT$no_tab_M])
agree_ATO
```

### Articles with baseline table
```{r}
length(agree_ATS$tab_sig_R) ## Total
length(agree_ATS$tab_sig_R[agree_ATS$tab_sig_R < 5]) ## Have sig test
subt = subset(agree_ATS, tab_sig_R == 5)
length(subt$Article[subt$no_tab_R < 4])

sub05_T = subset(agree_ATS, Year_R == 1)

length(sub05_T$tab_sig_R) ## 2005
length(sub05_T$tab_sig_R[sub05_T$tab_sig_R < 5]) ## Have sig test for 2005

table(sub05_T$N_R[sub05_T$tab_sig_R < 5]) 

subt_05 = subset(sub05_T, tab_sig_R == 5)
length(subt_05$Article[subt_05$no_tab_R < 4])

table(subt_05$N_R[subt_05$no_tab_R < 4])
table(subt_05$N_R[subt_05$no_tab_R == 4])

sub15_T = subset(agree_ATS, Year_R == 3)

table(sub15_T$N_R[sub15_T$tab_sig_R < 5]) 

length(sub15_T$tab_sig_R) ## 2015
length(sub15_T$tab_sig_R[sub15_T$tab_sig_R < 5]) ## Have sig test for 2015

subt_15 = subset(sub15_T, tab_sig_R == 5)
length(subt_15$Article[subt_15$no_tab_R < 4])

table(subt_15$N_R[subt_15$no_tab_R < 4])
table(subt_15$N_R[subt_15$no_tab_R == 4])
```

### Articles without baseline table
```{r}
length(agree_ATT$no_tab_R) ## Total
length(agree_ATT$no_tab_R[agree_ATT$no_tab_R < 4]) ## Text reference to sig test

sub05_N = subset(agree_ATT, Year_R == 1)

length(sub05_N$no_tab_R) ## 2005
length(sub05_N$no_tab_R[sub05_N$no_tab_R < 4]) ## Have sig test for 2005

table(sub05_N$N_R[subt_05$no_tab_R < 4])
table(sub05_N$N_R[subt_05$no_tab_R == 4])

sub15_N = subset(agree_ATT, Year_R == 3)

length(sub15_N$no_tab_R) ## 2015
length(sub15_N$no_tab_R[sub15_N$no_tab_R < 4]) ## Have sig test for 2015

table(sub15_N$N_R[subt_05$no_tab_R < 4])
table(sub15_N$N_R[subt_05$no_tab_R == 4])
```

a1 = read.csv("C:/Users/RLP/Documents/Word Documents/Biostatistics/Data Sets/Articles.csv")
a2 = read.csv("C:/Users/RLP/Documents/Word Documents/Biostatistics/Data Sets/Articles JK Added.csv")
a3 = a1$Article[!a1$Article%in%a2$Article]

write.csv(a3$Article, file = "C:/Users/RLP/Documents/Word Documents/Biostatistics/Data Sets/ArticlesRCT.csv")

### To read the variable values in the dataset:
For many variable names, _R and _M refer to answers submitted by Ross and Matt, respectively.

Name: 1 is Ross, 3 is Matt

Type: 1 is individual RCT, 2 is CRCT by Team, 3 is CRCT not by Team, 5 is none, 6 is crossover

N: 1 is < 50, 2 is 50-100, 3 is 101-150, 4 is 401-500, 5 is > 500, 6 is 201-300, 7 is 301-400

Table: 1 is has baseline covariate table, 2 is no

tab_sig: For question "Are p-values presented..." 1 is p-value, 2 is confidence interval, 3 is text, 4 is sig referenced, 5 is no

no_tab: For question "If no...", 1 is p-value, 2 is confidence interval, 3 is text, 4 is no